---
title: "Day 5 Session 1"
author: "Heather Childers"
format: 
    html:  
      code-fold: true
      code-summary: "show me the code"
editor: visual

execute: 
  warning: false
---

YAML:

execute: Warning: false (removes warnings from rendered document)

## Probability and Stats

```{r}
library(tidyverse)
```

### Star Wars Dataset

-   Look at the first 6 lines of code

-   find the dimensions of starwars

-   make a histogram of character heights

-   make a scatterplot of height vs weight

```{r}
head(starwars)

dim(starwars)
```

```{r}
ggplot(data=starwars, aes(x = height)) +
  geom_histogram()


```

```{r}
ggplot(data=starwars, aes(x=height, y=mass))+
  geom_point()
```

### Calculate Summary Statistics

mean()

sd()

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)
mean_weight <- mean(starwars$mass, na.rm = TRUE)

mean_height
mean_weight

sd_height <- sd(starwars$height, na.rm = TRUE )
sd_weight <- sd(starwars$mass, na.rm = TRUE)

sd_height
sd_weight
```

### In line reporting using code outputs

The mean of the distribution is `r mean_height` cm

with a standard dev of `r sd_height` cm
